A holographic approach to the six-dimensional superconformal index

### 2022-10-13 fivebranes/fact.tex
merge
remove CS

Like $\Obs_{sugra}$ in equation \eqref{eqn:sugraobs}, the factorization algebra $\Bar{\pi}_* \Obs_{sugra}$ is of the form $\clie^\bu(\cG)$.
Here, $\cG$ is a sheaf of $L_\infty$ algebras on $Z$ which is presented as the $C^\infty$-sections of an $\infty$-dimensional pro vector bundle.
To get a sense of the construction of this factorization algebra we take a brief excursion to a simpler situation related to branes in five-dimensional Chern--Simons theory.

In~\S \ref{s:twistedsugra} we recalled some features of a five-dimensional Chern--Simons type theory that Costello has shown to be the result of applying the $\Omega$-background to $M$-theory on a Taub--NUT space \cite{CostelloM5}.
In this setting fivebranes which hit the tip of the Taub--NUT are deformed into chiral defects supported along a Riemann surface~$C$ in the five-manifold. 
In analogy with our eleven-dimensional setup, we take the five-manifold to be $\R \times {\rm Tot}(K_C)$ with the deformed fivebranes wrapping the zero section.
Denote by $\Obs_{CS}$ the classical observables\footnote{We treat the theory classically as a perturbative theory on $\R \times {\rm Tot}(K_C)$.
We note that the theory is defined in terms of two parameters $\ep, \delta$ where $\delta$ is the Chern--Simons coupling and $\ep$ is the non-commutative parameter controlling the deformation quantization of the holomorphic symplectic manifold ${\rm Tot}(K_C)$.
For convenience we set both $\ep, \delta$ to be one.}
of the non-commmutative five-dimensional Chern--Simons theory on $\R \times {\rm Tot}(K_C)$.
Let 
\beqn
\pi \colon \R \times {\rm Tot}(K_C) \to C
\eeqn
be the natural projection and consider the factorization algebra $\pi_* \Obs_{CS}$ on $C$.

Notice that there is a $U(1)$ action on the fields of the five-dimensional theory induced by the $U(1)$ action on the five-manifold which scales the fiber of~$K_C$.
Using this we can look at the subfactorization algebra 
\beqn\label{eqn:taylor1a}
\Bar{\pi}_* \Obs_{CS} \subset \pi_* \Obs_{CS}
\eeqn
which to an open set $U \subset C$ assigns the complex of observables in $\Obs_{CS} (\pi^{-1} U)$ which are finite sums of integral eigenvectors for this $U(1)$ action.

For the rank one abelian gauge group, the space of fields of the five-dimensional theory on $\R \times {\rm Tot}(K_C)$ is
\[
\Omega^\bu(\R) \otimes \Omega^{0,\bu}({\rm Tot}(K_C)) [1] .
\]
The interaction is encoded by the symplectic structure on ${\rm Tot}(K_C)$.
%For simplicity, let us assume that the canonical bundle on $C$ is trivializable. 
For $U \subset C$, the complex of observables is given in terms of the Lie algebra cohomology
\[
(\pi_* \Obs_{CS})(U) \simeq \clie^\bu \left(\Omega^{0,\bu}(p^{-1}U)\right)
\]
where $p \colon K_C \to C$.
The Chevalley--Eilenberg complex is taken with respect to the dg Lie algebra structure coming from the holomorphic Poisson structure on the total space of~$K_C$. 
If $U$ is a trivializing cover then
\[
(\pi_* \Obs_{CS})(U) \simeq \clie^\bu \left(\Omega^{0,\bu}(C) \otimes \cO^{hol}(\C)\right) .
\]
On the other hand, we have
\[
(\Bar{\pi}_* \Obs_{CS})(U) \simeq \clie^\bu\left(\Omega^{0,\bu}(C) [[w]] \right) .
\]
Here, $w$ plays the role of a formal coordinate on the fiber of $K_C$ and $w^{k}$ as parametrizes the weight $k$ eigenspace---locally, $w$ is simply the one-form $\d z$.
Using this notation, the embedding \eqref{eqn:taylor1a} is induced by the Taylor series expansion map $\cO(\C) \to \C[[w]]$.
The dg Lie algebra structure on $\Omega^{0,\bu}(C) [[w]]$ is given by the Moyal commutator. 
This is similar to the non-formal case---it is the natural bracket if we understand $\cO(C)[[w]]$ as functions on the formal neighborhood of the zero section in~$K_C$.

@@

Let us return to the situation of a complex three-fold $Z$ as submanifold the eleven-manifold~$\R \times \text{Tot}(K_{Z}^{1/2} \otimes \C^2)$. 
The construction of the restricted factorization algebra $\Bar{\pi}_* \Obs_{sugra}$ is completely similar to the simple case of five-dimensional Chern--Simons theory as we just discussed.

This time we consider the group $U(1) \times U(1)$ rotating the fibers of the rank two bundle $K_Z^{1/2} \otimes \C^2$. 
Using this we can define the subfactorization algebra 
\beqn\label{eqn:taylor1b}
\Bar{\pi}_* \Obs_{sugra} \subset \pi_* \Obs_{sugra}
\eeqn
which to an open set~$U \subset Z$ assigns the subcomplex of observables in~$\Obs_{sugra} (\pi^{-1} U)$ which are finite sums of integral eigenvectors for this $U(1) \times U(1)$ action.

By construction, the restricted factorization algebra is of the form
\[
\pi_*\Obs_{sugra} = \clie^\bu(\cG_Z) 
\]
where $\cG_Z$ is an infinite-rank local $L_\infty$ algebra on $Z$. 
Just as in the case of five-dimensional Chern--Simons theory, the embedding of factorization algebras \eqref{eqn:taylor1b} is induced by a partial Taylor expansion map
\[
\pi_* \cL_{sugra} \to \cG_Z .
\]

@@

\subsection{A finite $N$ conjecture}
\label{sec:factsummary}

>>>>

Like $\Obs_{sugra}$ in equation \eqref{eqn:sugraobs}, the factorization algebra $\Bar{\pi}_* \Obs_{sugra}$ is of the form $\clie^\bu(\cG)$.
Here, $\cG$ is a sheaf of $L_\infty$ algebras on $Z$ which is presented as the $C^\infty$-sections of an $\infty$-dimensional pro vector bundle.
%To get a sense of the construction of this factorization algebra we take a brief excursion to a simpler situation related to branes in five-dimensional Chern--Simons theory.

%\parsec[]
%
%In~\S \ref{s:twistedsugra} we recalled some features of a five-dimensional Chern--Simons type theory that Costello has shown to be the result of applying the $\Omega$-background to $M$-theory on a Taub--NUT space \cite{CostelloM5}.
%In this setting fivebranes which hit the tip of the Taub--NUT are deformed into chiral defects supported along a Riemann surface~$C$ in the five-manifold. 
%In analogy with our eleven-dimensional setup, we take the five-manifold to be $\R \times {\rm Tot}(K_C)$ with the deformed fivebranes wrapping the zero section.
%Denote by $\Obs_{CS}$ the classical observables\footnote{We treat the theory classically as a perturbative theory on $\R \times {\rm Tot}(K_C)$.
%We note that the theory is defined in terms of two parameters $\ep, \delta$ where $\delta$ is the Chern--Simons coupling and $\ep$ is the non-commutative parameter controlling the deformation quantization of the holomorphic symplectic manifold ${\rm Tot}(K_C)$.
%For convenience we set both $\ep, \delta$ to be one.}
%of the non-commmutative five-dimensional Chern--Simons theory on $\R \times {\rm Tot}(K_C)$.
%Let 
%\beqn
%\pi \colon \R \times {\rm Tot}(K_C) \to C
%\eeqn
%be the natural projection and consider the factorization algebra $\pi_* \Obs_{CS}$ on $C$. 
%
%Notice that there is a $U(1)$ action on the fields of the five-dimensional theory induced by the $U(1)$ action on the five-manifold which scales the fiber of~$K_C$.
%Using this we can look at the subfactorization algebra 
%\beqn\label{eqn:taylor1a}
%\Bar{\pi}_* \Obs_{CS} \subset \pi_* \Obs_{CS}
%\eeqn
%which to an open set $U \subset C$ assigns the complex of observables in $\Obs_{CS} (\pi^{-1} U)$ which are finite sums of integral eigenvectors for this $U(1)$ action.
%
%For the rank one abelian gauge group, the space of fields of the five-dimensional theory on $\R \times {\rm Tot}(K_C)$ is
%\[
%\Omega^\bu(\R) \otimes \Omega^{0,\bu}({\rm Tot}(K_C)) [1] .
%\]
%The interaction is encoded by the symplectic structure on ${\rm Tot}(K_C)$.
%%For simplicity, let us assume that the canonical bundle on $C$ is trivializable. 
%For $U \subset C$, the complex of observables is given in terms of the Lie algebra cohomology
%\[
%(\pi_* \Obs_{CS})(U) \simeq \clie^\bu \left(\Omega^{0,\bu}(p^{-1}U)\right)
%\]
%where $p \colon K_C \to C$.
%The Chevalley--Eilenberg complex is taken with respect to the dg Lie algebra structure coming from the holomorphic Poisson structure on the total space of~$K_C$. 
%If $U$ is a trivializing cover then
%\[
%(\pi_* \Obs_{CS})(U) \simeq \clie^\bu \left(\Omega^{0,\bu}(C) \otimes \cO^{hol}(\C)\right) .
%\]
%On the other hand, we have
%\[
%(\Bar{\pi}_* \Obs_{CS})(U) \simeq \clie^\bu\left(\Omega^{0,\bu}(C) [[w]] \right) .
%\]
%Here, $w$ plays the role of a formal coordinate on the fiber of $K_C$ and $w^{k}$ as parametrizes the weight $k$ eigenspace---locally, $w$ is simply the one-form $\d z$.
%Using this notation, the embedding \eqref{eqn:taylor1a} is induced by the Taylor series expansion map $\cO(\C) \to \C[[w]]$.
%The dg Lie algebra structure on $\Omega^{0,\bu}(C) [[w]]$ is given by the Moyal commutator. 
%This is similar to the non-formal case---it is the natural bracket if we understand $\cO(C)[[w]]$ as functions on the formal neighborhood of the zero section in~$K_C$.

@@

We are in the situation of a complex three-fold $Z$ embedded as a submanifold of the eleven-manifold~$\R \times \text{Tot}(K_{Z}^{1/2} \otimes \C^2)$. 
%The construction of the restricted factorization algebra $\Bar{\pi}_* \Obs_{sugra}$ is completely similar to the simple case of five-dimensional Chern--Simons theory as we just discussed.
Consider the group $U(1) \times U(1)$ rotating the fibers of the rank two bundle $K_Z^{1/2} \otimes \C^2$. 
Using this we can define the subfactorization algebra 
\beqn\label{eqn:taylor1b}
\Bar{\pi}_* \Obs_{sugra} \subset \pi_* \Obs_{sugra}
\eeqn
which to an open set~$U \subset Z$ assigns the subcomplex of observables in~$\Obs_{sugra} (\pi^{-1} U)$ which are finite sums of integral eigenvectors for this $U(1) \times U(1)$ action.

By construction, the restricted factorization algebra is of the form
\[
\Bar{\pi}_*\Obs_{sugra} = \clie^\bu(\cG_Z) 
\]
where $\cG_Z$ is an infinite-rank local $L_\infty$ algebra on $Z$. 
The embedding of factorization algebras \eqref{eqn:taylor1b} is induced by a partial Taylor expansion map
\[
\pi_* \cL_{sugra} \to \cG_Z .
\]

@@

\subsection{Finite $N$ factorization algebras}
\label{sec:factsummary}
